---
title: "690 Project"
author: "Bianca Doone"
date: "April 26, 2018"
output: pdf_document
---

```{r, warning=FALSE, echo=FALSE, message=FALSE}
library(leaps)
library(glmnet)

nhanes0 = read.csv("C:/Users/bdoone/Downloads/nhanes2.csv")
nhanes2 = nhanes0[,c(2,4,5,6,8,11,12,13,15,16,17,18,19,20,21,22,26,28,29,31,32,33,34)]
chd_df = nhanes2[,c(1:12, 15:23)]
ha_df = nhanes2[,c(1:11, 13, 15:23)]
stroke_df = nhanes2[,c(1:11, 14:23)]

chd_df$chd = chd_df$chd-1
ha_df$heartattack = ha_df$heartattack-1
stroke_df$stroke = stroke_df$stroke-1

chd_glm_full = glm(chd~., data = chd_df, family = "binomial")
chd_glm_null = glm(chd~1, data = chd_df, family = "binomial")
```
gender, age,ethnicity,bmi, bp sys, bp di, indfmmpi, slq060


#Coronary Heart Disease
Best Subset
```{r}
bestchd = regsubsets(chd~.,data = chd_df, nvmax = 23, really.big = T)
best.sum = summary(bestchd)
best.sum$rss

```

age, race, height, pulsetype, hdl, heartattack, stroke, modrecract, ldl

Forward Subset
```{r}
forwardchd = regsubsets(chd~., data =chd_df, nvmax = 23, method = "forward")
forward.sum = summary(forwardchd)
forward.sum$rss

f2chd = step(chd_glm_null, direction = "forward")
b2chd = step(chd_glm_full, direction = "backward")

summary(f2chd)
```

age, race, height, totchol, heartattack, stroke, modrecract, triglyceride, agecat

Backward Subset
```{r}
backwardchd = regsubsets(chd~., data = chd_df, nvmax = 23, method = "backward")
backward.sum = summary(backwardchd)
backward.sum$rss
```

age, bmi, weight, totchol, heartattack, stroke, modrecract, triglyceride, bmicat

plots
```{r}
plot(best.sum$rss, xlab = "Number of Variables",
     ylab = "RSS", type = "l",
     main = "Coronary Heart Disease")
lines(forward.sum$rss, col = "blue")
lines(backward.sum$rss, col = "red")
legend(13,118,legend = c("Best", "Forward", "Backward"), col = c("black", "blue", "red"), lty = 1)

```


#Heart Attack

Best Subset
```{r}
bestha = regsubsets(heartattack~.,data = ha_df, nvmax = 23, really.big = T)
best.sum2 = summary(bestha)
best.sum2$rss

```

age, race, weight, waistcirc, diabetes, chd, stroke, ldl, pircat

Forward Subset
```{r}
forwardha = regsubsets(heartattack~., data =ha_df, nvmax = 23, method = "forward")
forward.sum2 = summary(forwardha)
forward.sum2$rss
```

height, diabetes, chd, stroke, modworkact, sleephrs, ldl, agecat, pircat

Backward Subset
```{r}
backwardha = regsubsets(heartattack~., data = ha_df, nvmax = 23, method = "backward")
backward.sum2 = summary(backwardha)
backward.sum2$rss
```

race, weight, wasitcirc, diabetes, chd, stroke, ldl, agecat, pircat

plots
```{r}
plot(best.sum2$rss, xlab = "Number of Variables",
     ylab = "RSS", type = "l",
     main = "Heart Attack")
lines(forward.sum2$rss, col = "blue")
lines(backward.sum2$rss, col = "red")
legend(13,139,legend = c("Best", "Forward", "Backward"), col = c("black", "blue", "red"), lty = 1)
```


#Stroke

Best Subset
```{r}
beststr = regsubsets(stroke~.,data = stroke_df, nvmax = 23, really.big = T)
best.sum3 = summary(bestha)
best.sum3$rss

```

age, race, weight, waistcirc, diabetes, chd, stroke, ldl, pircat

Forward Subset
```{r}
forwardstr = regsubsets(stroke~., data =stroke_df, nvmax = 23, method = "forward")
forward.sum3 = summary(forwardstr)
forward.sum3$rss
```

height, diabetes, chd, stroke, modworkact, sleephrs, ldl, agecat, pircat

Backward Subset
```{r}
backwardstr = regsubsets(stroke~., data = stroke_df, nvmax = 23, method = "backward")
backward.sum3 = summary(backwardstr)
backward.sum3$rss
```

race, weight, wasitcirc, diabetes, chd, stroke, ldl, agecat, pircat

plots
```{r}
plot(best.sum3$rss, xlab = "Number of Variables",
     ylab = "RSS", type = "l",
     main = "Stroke", ylim = c(92.5,140))
lines(forward.sum3$rss, col = "blue")
lines(backward.sum3$rss, col = "red")
legend(12,120,legend = c("Best", "Forward", "Backward"), col = c("black", "blue", "red"), lty = 1)
```



##Notes:

Based on: gender, race, education, marital, bmi, waistcirc, pulsetype, gh, totchol, diabetes, drinks, cancer, modworkact, sleepdisorder, smoker, triglyceride, phq, sbp, dbp

###CHD: 15 variable model
ALL: gender, marital, bmi, waistcirc, pulsetype, gh, totchol, drinks, cancer, modworkact, sleepdisorder, smoker, triglyceride, sbp, dbp

```{r}
best.sum$rss[15]
forward.sum$rss[15]
backward.sum$rss[15]

best.sum$rsq[15]
forward.sum$rsq[15]
backward.sum$rsq[15]
```


###HA: 15 Variable Model
ALL: race, education, marital, bmi, waistcirc, gh, totchol, drinks, cancer, modworkact, sleepdisorder, triglyceride, phq, sbp, dbp

```{r}
best.sum2$rss[15]
forward.sum2$rss[15]
backward.sum2$rss[15]

best.sum2$rsq[15]
forward.sum2$rsq[15]
backward.sum2$rsq[15]
```



###STR: 5 Variable Model

BSS: bmi, waistcirc, totchol, modworkact, sleepdisorder (really bad compared to other two)

FS: education, diabetes, drinks, cancer, phq

BS: education, waistcirc, drinks, cancer, phq

```{r}
best.sum3$rss[5]
forward.sum3$rss[5]
backward.sum3$rss[5]

best.sum3$rsq[15]
forward.sum3$rsq[15]
backward.sum3$rsq[15]
```


#Lasso and Ridge
```{r}
x.chd = model.matrix(chd~., chd_df)[-1]
y.chd = chd_df$chd
ridge.chd = glmnet(x.chd, y.chd, family = "binomial", alpha=0)

```


















